---
title: "Shape_Aggerator"
author: "Peter Dudley"
date: "9/28/2021"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# knitr::opts_knit$set(root.dir = normalizePath(".."))
```

# Sample all shape files into the grid

This script takes multiple shape files and prints out the csv with the grid 

Start with the grid  
```{r}
#____________________________________________________________________#
##### Options #####
# What resolution is the grid you are using
resolution = 200
# what is the max buffer distance of the grid
max_buffer = 500
# Do you want the plots to show up
show_plots = 1
# select the number of computer cores to use in analysis
number_cores = 8
# Location of grid
grid_folder = "./temporary/R/"
# Location of the shape folder
shape_folder = "./data/GIS/example_shapes_1/"
# Where to save the output
output_folder = "./temporary/NetLogo/"
#____________________________________________________________________#
```

Load the necessary libraries and functions
```{r, message=FALSE, warning=FALSE, include=FALSE}
# the simple features library for most of the shape file stuff
library(sf)
# leaflet for plotting shapefiles
library(leaflet)
# you know why
library(tidyverse)
# deal with most of the rater calculations
library(raster)
# to smooth the center line of the river
library(smoothr)
# the viridis color map
library(viridis)
# a faster way to do raster sampling with shape files
library(exactextractr)
# Library to parallelize purrr
library(furrr)
# Library to join graphs
library(patchwork)

# Make sure dplyr select is the default
select = dplyr::select

# Setup furrr
future::plan(multisession, workers = number_cores)
future.seed = TRUE

# Load the function to sample shapes on the grid
source("./scripts/R/spatial_inputs/scripts/Sample_Shapes_Functions.R")
```

Load the necessary data
```{r}
# load the river grid
river_grid = readRDS(paste0(grid_folder, "river_grid_", resolution, "_", max_buffer, ".rds"))
# Load the cover file
cover_shape = st_read(paste0(shape_folder, "cover.shp"), quiet = TRUE) 
# Load the food zone file
food_shape = st_read(paste0(shape_folder, "food.shp"), quiet = TRUE) 
# Load the vegetation bank file
vegetation_shape = st_read(paste0(shape_folder, "vegetation.shp"), quiet = TRUE) 
# Load the substrate bank file
substrate_shape = st_read(paste0(shape_folder, "substrate.shp"), quiet = TRUE) 
```

Make a list of the shape files and variabels 
```{r}
variables = list("cover", "food", "vegetation", "substrate")
shape_files = list(cover_shape, food_shape, vegetation_shape, substrate_shape)
```


Run the function and reduce the results to get one shapefile
```{r}
sampeled_shapes = sample_all_shapes(river_grid, shape_files, variables)
```

Convert the sampe file to CSV file
```{r}
shapes_csv = sampeled_to_csv(sampeled_shapes) 
```

Show shape sample 1 
```{r, fig.show="hold"}
if(show_plots){

ggplot(data = sampeled_shapes) +
    theme_classic() +
    geom_sf(aes(fill = cover), color = NA) +
    scale_fill_viridis()
}
```

Show shape sample 2 
```{r, fig.show="hold"}
if(show_plots){

ggplot(data = sampeled_shapes) +
    theme_classic() +
    geom_sf(aes(fill = Cover), color = NA) +
    scale_fill_viridis()
}
```

Show gridded nature of the sampeling by zooming in
```{r, fig.show="hold"}
if(show_plots){

ggplot(data = sampeled_shapes) +
    theme_classic() +
    geom_sf(aes(fill = Cover), color = NA) +
    xlim(554000, 554200)+
    ylim(4484700, 4485000)+
    scale_fill_viridis()
}
```

Show shape sample 3 
```{r, fig.show="hold"}
if(show_plots){

ggplot(data = sampeled_shapes) +
    theme_classic() +
    geom_sf(aes(fill = Zones), color = NA) +
    scale_fill_viridis()
}
```

