---
title: "MR equations"
author: "Jesse"
date: "2022-08-08"
output: html_document
---



clear environment and load in packages 







```{r}



# clearing environment:
rm(list = ls())


library(styler)
library(visreg)
library(lme4)
library(tidyverse)
library(lubridate)
library(openxlsx)
library(viridis)
library(broom)
library(visreg)

library(mosaic)
library(car)
library(rgl)
library(nlstools)
library(ggpubr)
library(grid)
library(effects)
library(DHARMa)
library(stats)
library(MuMIn)


```



This code first fits the specified metabolic rate GLM for each species' dataset specified. The second half of the code just creates exportable R formulae for each species' GLM, and ensures that they produce the same prediction values. If the points don't track the one-one line, the GLM and the formulae don't match- you have to specify each formula manually.



Loading and subsetting data

  Specify the species by unhashing the name below. Optional toggles for swim speed and temperature. The working directory must include the file "respiration_data.xlsx".
  



```{r}





################### add data repository

setwd("C://Users/jesse/OneDrive/Documents/UCSC-DESKTOP-OD7AB1S/data sources/FHAST Data/respiration/")

########################   USER INPUTS   ####################

# USER INPUT: designating species
# OPTIONS: "Chinook", "Green  sturgeon", "Steelhead"


############# SPECIES



 species_name <- "Chinook"
#  species_name <- "Green sturgeon"
# species_name <- "Steelhead"
#   species_name <- "multiple sturgeon"
#  species_name <- "all together"





 

############ VARIABLES
toggle_swimspeed <- T

toggle_temp <- T


############# LIFE STAGE

# options:REMOVE HASH FROM ONE OF THE FOLLOWING:

#  life_stage_name = "egg"

# life_stage_name = "endogenous feeders"

#  life_stage_name = "exogenous feeders and small juveniles"

# life_stage_name = "large juveniles and adults"

    life_stage_name <- "exogenous feeders"

#      life_stage_name  <-     "yolk-sac larvae"



############### FEEDING MODE


 feeding_mode  <- "exogenous"
# feeding_mode <- "endogenous"


############# LOAD INPUT DATA




met_data <- read.xlsx(
  xlsxFile = "respiration_data.xlsx",
  sheet = species_name,
  na.strings = "NA"
)






```


  Subsetting for quality control and for desired feeding mode

    data flag of 1 = good data
    data flag of 2 = somewhat questionable or less desirable data, ie fish were cannulated
    data flag of 3 = don't use for MR parameter calculation! Data includes effects of an experimental treatment or is otherwise considered very suspect. See
    

```{r}






######### cleaning up NA's/missing data etc

met_data <- subset(met_data, subset = met_data$data_quality == 1)



#-9999 used in master datasheet to denote missing values
# script below should turn them all into NA's



# setting swimspeed to 0 where it was not studies
#   met_data$swimspeed_bodylengths_per_second[met_data$swimspeed_bodylengths_per_second== -9999]<- 0

met_data <- subset(met_data, met_data$mass_g != -9999)
met_data <- subset(met_data, met_data$mr_mgo2_per_h != -9999)
met_data <- subset(met_data, met_data$temperature_c != -9999)

if (feeding_mode == "exogenous") {
  

met_data <- subset(met_data, met_data$swimspeed_bodylengths_per_second != -9999)

}


### removes eggs

met_data <- subset(met_data, met_data$life_stage != "egg" & met_data$life_stage != "embryo")



# converts missing data to NA for R
met_data[met_data == -9999] <- NA


# mutate step adds a column for metajoules of energy used per day

met_data <- met_data %>%
  mutate(met_j_per_day = mr_mgo2_per_h * 24 * 19.3 * 22.4 / 32)


met_data <- met_data %>%
  mutate(mr_go2_per_day = mr_mgo2_per_h * 24/1000)


met_data <- met_data %>%
  mutate(study = paste(author, year, journal, sep = ", "))

##FBE4 uses 13,560J/g of oxygen per day


met_data <- met_data %>%
  mutate(j_per_day_dif_occ = mr_go2_per_day * 13560)

plot(met_data$met_j_per_day~met_data$j_per_day_dif_occ) 
abline(a = c(0,1))


#so its not a calculation issue, it seems

#round mass


met_data <- met_data %>%
  mutate(mass_g_rounded = round(mass_g, 2))



met_data$mass_g <- met_data$mass_g_rounded

met_data <- met_data %>%
  mutate(met_j_per_day_per_g = met_j_per_day / mass_g)

met_data <- met_data %>%
  mutate(sqrt_swimspeed_bodylengths_per_second = sqrt(met_data$swimspeed_bodylengths_per_second))


### adding log temperature
met_data <- met_data %>%
  mutate(log_temperature_c = log(met_data$temperature_c))


### adding log temperature
met_data <- met_data %>%
  mutate(log_mass_g = log(met_data$mass_g))

# Change histogram plot line colors by groups


# plot of mass vs MR colored by author


    ```


Subsetting for endogenous/exogenous feeders


```{r}


if (feeding_mode  == "endogenous") {
  


### selecting only exogenous feeders
met_data <- subset(met_data, subset = met_data$exogenous_or_endogenous == "endogenous")



}


if (feeding_mode  == "exogenous") {
  


### selecting only exogenous feeders
met_data <- subset(met_data, subset = met_data$exogenous_or_endogenous == "exogenous")






}




```          



This chunk adds a new column for metabolic_category_specific, which here is the smolting status of Chinook/Steelhead and seawater tolerance for green sturgeon.




```{r}

############# Green sturgeon  ############

if (species_name == "Green sturgeon") {


  # creating a metabolic category factor

  met_data$metabolic_category_specific <- NA

  met_data$metabolic_category_specific[(met_data$age_dph < 134) & (met_data$exogenous_or_endogenous == "exogenous")] <- "SW intolerant (< 134 dph)"

  met_data$metabolic_category_specific[(met_data$age_dph >= 134) & (met_data$exogenous_or_endogenous == "exogenous")] <- "SW tolerant (> 134 dph)"

  met_data$metabolic_category_specific[(met_data$exogenous_or_endogenous == "endogenous") & (met_data$life_stage != "egg") & (met_data$life_stage != "embryo")] <- "larvae (endg.)"


  met_data$metabolic_category_specific[(met_data$life_stage == "egg") | (met_data$life_stage == "embryo")] <- "eggs"
}










############# Steelhead  ############

if (species_name == "Steelhead") {





  # creating a metabolic category factor

  met_data$metabolic_category_specific <- NA

  met_data$metabolic_category_specific[(met_data$mass_g < 33) & (met_data$exogenous_or_endogenous == "exogenous")] <- "pre-smolt (< 33g)"

  met_data$metabolic_category_specific[(met_data$mass_g >= 33) & (met_data$exogenous_or_endogenous == "exogenous")] <- "post-smolt (> 33g)"


  met_data$metabolic_category_specific[(met_data$mass_g >= 33) & (met_data$life_stage == "adult")] <- "adults"



  met_data$metabolic_category_specific[(met_data$exogenous_or_endogenous == "endogenous") & (met_data$life_stage != "egg") & (met_data$life_stage != "embryo")] <- "larvae (endg.)"


  met_data$metabolic_category_specific[(met_data$life_stage == "egg") | (met_data$life_stage == "embryo")] <- "eggs"


  ### source for 30g cutoff: Pevan et al 1994.
}





############# Chinook  ############

if (species_name == "Chinook") {




  # creating a metabolic category factor

  met_data$metabolic_category_specific <- NA

  met_data$metabolic_category_specific[(met_data$mass_g < 7.2) & (met_data$exogenous_or_endogenous == "exogenous")] <- "pre-smolt (< 7.2g)"

  met_data$metabolic_category_specific[(met_data$mass_g >= 7.2) & (met_data$exogenous_or_endogenous == "exogenous")] <- "post-smolt (> 7.2g)"


  met_data$metabolic_category_specific[(met_data$mass_g >= 7.2) & (met_data$life_stage == "adult")] <- "adults"



  met_data$metabolic_category_specific[(met_data$exogenous_or_endogenous == "endogenous") & (met_data$life_stage != "egg") & (met_data$life_stage != "embryo")] <- "larvae (endg.)"


  met_data$metabolic_category_specific[(met_data$life_stage == "egg") | (met_data$life_stage == "embryo")] <- "eggs"


  ### source for 7.2g cutoff:
}



# McEwan uses "smolts" for fish above ~70mm fork length
```
















GREEN STURGEON GLM

```{r}

if (species_name == "Green sturgeon") {
  


green_sturgeon_respiration_glm <- glm(formula = log(met_j_per_day) ~ log(mass_g) + log(temperature_c) + 
    swimspeed_bodylengths_per_second + log(mass_g):log(temperature_c) + 
    1, data = met_data, na.action = "na.fail")





##################  OFFICIAL GS EQUATION

## make exportable equation  


  GS_equation <- function( log_met_j_per_day,
                                   mass_g,
                                   temperature_c,            swimspeed_bodylengths_per_second)
                        
                        
                        {
               (-2.7383) +
               (1.5702   * log(mass_g)) +
               (2.5616   * log(temperature_c)) +
               (2.1125   * swimspeed_bodylengths_per_second  ) +
               (-0.2562 * log(mass_g) * log(temperature_c)) 
  
                          
}

  
  
#### test if glm predictions and equation predictions are the same  
  
  GS_prediction_testdf <- NA

  mass_g <- met_data$mass_g
  
  temperature_c <- met_data$temperature_c 
  
  swimspeed_bodylengths_per_second <-
    met_data$swimspeed_bodylengths_per_second


GS_prediction_testdf <- data.frame(mass_g, temperature_c, swimspeed_bodylengths_per_second)

  #add predictions from glm itself
  
  GS_glm_predictions_log_met_j_per_day <- predict(green_sturgeon_respiration_glm, newdata = GS_prediction_testdf)


  GS_equation_predictions_log_met_j_per_day <- GS_equation(mass_g = mass_g, temperature_c =temperature_c, swimspeed_bodylengths_per_second = swimspeed_bodylengths_per_second)

  
  
  
  round(GS_glm_predictions_log_met_j_per_day, 2)  == round(GS_equation_predictions_log_met_j_per_day, 2)


    plot(GS_glm_predictions_log_met_j_per_day ~ GS_equation_predictions_log_met_j_per_day)
    abline(a = c(0,1))
    
    
}

```



Steelhead GLM




```{r}

if (species_name== "Steelhead") {
  


steelhead_glm <- glm(formula = log(met_j_per_day) ~ log(mass_g) + log(temperature_c) + 
    swimspeed_bodylengths_per_second + log(mass_g):swimspeed_bodylengths_per_second + 
    1, data = met_data, na.action = "na.fail")




steelhead_glm

##################  OFFICIAL SH EQUATION

## make exportable equation  


  SH_equation <- function( log_met_j_per_day,
                                   mass_g,
                                   temperature_c,            swimspeed_bodylengths_per_second)
                        
                        
                        {
               (2.739731) +
               (0.873066   * log(mass_g)) +
               (0.621671   * log(temperature_c)) +
               (0.101906   * swimspeed_bodylengths_per_second  ) +
               (0.042006 * (log(mass_g) * swimspeed_bodylengths_per_second))
  
                          
}

  
  
#### test if glm predictions and equation predictions are the same  
  
  SH_prediction_testdf <- NA

  mass_g <- met_data$mass_g
  
  temperature_c <- met_data$temperature_c 
  
  swimspeed_bodylengths_per_second <-
    met_data$swimspeed_bodylengths_per_second


SH_prediction_testdf <- data.frame(mass_g, temperature_c, swimspeed_bodylengths_per_second)

  #add predictions from glm itself
  
  SH_glm_predictions_log_met_j_per_day <- predict(steelhead_glm, newdata = SH_prediction_testdf)


  SH_equation_predictions_log_met_j_per_day <- SH_equation(mass_g = mass_g, temperature_c =temperature_c, swimspeed_bodylengths_per_second = swimspeed_bodylengths_per_second)

  
  
  
  round(SH_glm_predictions_log_met_j_per_day, 2)  == round(SH_equation_predictions_log_met_j_per_day, 2)


    plot(SH_glm_predictions_log_met_j_per_day ~ SH_equation_predictions_log_met_j_per_day)
    abline(a = c(0,1))
    
}

```







Chinook GLM 




```{r} 


if (species_name== "Chinook") {


chinook_resp_glm <- glm(formula = log(met_j_per_day) ~ log(mass_g) + sqrt(swimspeed_bodylengths_per_second) + 
    temperature_c + log(mass_g):sqrt(swimspeed_bodylengths_per_second) + 
    log(mass_g):temperature_c + 1, data = met_data, na.action = "na.fail")
 


 





##################  OFFICIAL CS EQUATION

## make exportable equation  


  CS_equation <- function( log_met_j_per_day,
                                   mass_g,
                                   temperature_c,            swimspeed_bodylengths_per_second)
                        
                        
                        {
               (3.487260) +
               (0.839921   * log(mass_g)) +
               (0.084116   * temperature_c) +
               (-0.736397   * sqrt(swimspeed_bodylengths_per_second) ) +
      
               (0.324398 * (log(mass_g) *  sqrt(swimspeed_bodylengths_per_second))) + 
                 (-0.007797 * (log(mass_g) * temperature_c))
  
                          
}

  
  
#### test if glm predictions and equation predictions are the same  
  
  CS_prediction_testdf <- NA

  mass_g <- met_data$mass_g
  
  temperature_c <- met_data$temperature_c 
  
  swimspeed_bodylengths_per_second <-
    met_data$swimspeed_bodylengths_per_second


CS_prediction_testdf <- data.frame(mass_g, temperature_c, swimspeed_bodylengths_per_second)

  #add predictions from glm itself
  
  CS_glm_predictions_log_met_j_per_day <- predict(chinook_resp_glm, newdata = CS_prediction_testdf)


  CS_equation_predictions_log_met_j_per_day <- CS_equation(mass_g = mass_g, temperature_c =temperature_c, swimspeed_bodylengths_per_second = swimspeed_bodylengths_per_second)

  
  
  
  round(CS_glm_predictions_log_met_j_per_day, 2)  == round(CS_equation_predictions_log_met_j_per_day, 2)


    plot(CS_glm_predictions_log_met_j_per_day ~ CS_equation_predictions_log_met_j_per_day)
    abline(a = c(0,1))








}









```




