---
output:  html_document
number_sections: true
title: | 
  | FHAST Habitat Summary
header-includes:
    - \usepackage{setspace}\singlespacing
    - \usepackage{float}
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=0.2in
fontsize: 16pt
fig_caption: yes
indent: true
---
 <font size="4">

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, knitr::opts_chunk$set(warning = FALSE, message = FALSE))
library(here)

# Load Libraries
source(here("scripts","main","load_libraries.R"))

# Load some common functions used in running FHAST
# Load some file handling functions
source(here("scripts", "fhast_functions", "fhast_file_functions.R"))
# Load some file basic math functions
source(here("scripts", "fhast_functions", "fhast_math_functions.R"))
# Load some file basic biology functions
source(here("scripts", "fhast_functions", "fhast_biology_functions.R"))
# Load some plotting functions
source(here("scripts", "fhast_functions", "fhast_plot_functions.R"))

# Sets up the file structure for FHAST run
source(here("scripts", "main", "set_fhast_file_structure.R"))

# Run the initialization 
source(here("scripts","main","initialize_fhast.R"))

# load all the input files and make basic parameter files
# also do some basic checking of files
# need to load pathfinder finding first for adult parameters
source(here("scripts","migration", "pathfinding_functions.R"))
source(here("scripts","format_parameters","load_convert_parameters.R"))

input_data <- load_text_file(file.path(input_folder, fhast_config_file))

simulation_name = input_data["run name",]
```

```{r load_data, include=FALSE}
summary_stats = readRDS(file = here("temporary",  "summary_stats_table.rds")) 

fish_summary_stats = readRDS(file = here("temporary",  "summary_fish_stats_table.rds"))

cover_scatter_plot = here("temporary",  "cover_scatter_plot.png")

cover_facet_map = here("temporary",  "cover_facet_map.png")

cover_facet_hist = here("temporary",  "cover_facet_hist.png")

cutoff_map = here("temporary",  "cutoff_map.png")

heat_map_plot = here("temporary",  "depth_velocity_heatmap.png")

fish_met_plot = here("temporary",  "metabolic_map.png")

fish_net_energy_plot = here("temporary",  "net_energy_map.png")

```

```{r pre_rrocess, include=FALSE}
predator_list =  unique(pred_model_params$species)
fish_list = unique(fish_parm$specie)
n = 0
```

### Simulation name: `r simulation_name`
***
## Tabular Outputs 

```{r print_summary_stats, echo = FALSE}
kable(summary_stats, caption = paste0("The habitat summary statistics. Units vary and are given next to each item name. CBC stands for cover bellow cuttoff percent which is the precent of area which is bellow the depth (", habitat_parm$dep_cutoff, " m) and velocity (", habitat_parm$vel_cutoff, " m/s) cuttoffs and has cover"))
```

```{r print_fish_summary_stats, echo = FALSE}
fish_count <- length(unique(fish_summary_stats$species))

kable(fish_summary_stats,
      caption = paste0("The fish summary statistics for both juvenile and adult life stages of the ", fish_count, " specie(s) of fish."),
      col.names = c("Species", "Life Stage", "Metabolic Rate (j/day)"))
```

\newpage
## Figures Outputs

```{r print_cover_figure, echo = FALSE, out.width = "100%", fig.align="center"}
knitr::include_graphics(cover_scatter_plot)
```

**Fig. `r (n = n + 1)`** The amount of cover area that is is water shallower then the cutoff (`r habitat_parm$dep_cutoff` m) for the level of flows present in the simulation. <br><br><br><br>


```{r print_facet_map, echo = FALSE, out.width = "100%", fig.align="center"}
knitr::include_graphics(cover_facet_map)
```

**Fig. `r (n = n + 1)`** The fraction of an area that is undercover separated by sections that are on average above or bellow the depth and velocity cutoffs (`r habitat_parm$dep_cutoff` m and `r habitat_parm$vel_cutoff` m/s respectively). <br><br><br><br>

```{r print_facet_hist, echo = FALSE, out.width = "100%", fig.align="center"}
knitr::include_graphics(cover_facet_hist)
```

**Fig. `r (n = n + 1)`** The density histograms of the area that is undercover separated by sections that are on average above or bellow the depth and velocity cutoffs (`r habitat_parm$dep_cutoff` m and `r habitat_parm$vel_cutoff` m/s respectively). <br><br><br><br>

```{r print_heatmap_figure, echo = FALSE, out.width = "100%", fig.align="center"}
knitr::include_graphics(heat_map_plot)
```

**Fig. `r (n = n + 1)`** A heat map showing the fraction of area at set average depths and velocities over the time of the simulation (`r daily_inputs["start date",]` to `r daily_inputs["end date",]`) . <br><br><br><br>

```{r print_fish_met_figure, echo = FALSE, out.width = "100%",  fig.align="center" }
knitr::include_graphics(fish_met_plot)
```

**Fig. `r (n = n + 1)`** A set of maps showing the metabolic rate for both the juvenile and adult life stage of the simulated species of fish (`r fish_list`) if the fish swam at the water velocity and temperature of the cell for 24 hours. <br><br><br><br>

```{r print_fish_energy_figure, echo = FALSE, out.width = "100%",  fig.align="center", fig.cap = "The net energy of the fish."}
knitr::include_graphics(fish_net_energy_plot)
```

**Fig. `r (n = n + 1)`** A set of maps showing the net energy budget for both the juvenile and adult life stage of the simulated species of fish (`r fish_list`) if the fish swam at the water velocity and temperature of the cell for 24 hours and consumed food. <br><br><br><br>

\newpage
## Appendix
### Run inputs
The main input file:
```{r, echo=FALSE}
cat(readLines(file.path(input_folder, fhast_config_file)), sep = '\n')
```
---

The daily input file:
```{r, echo=FALSE, }
cat(readLines(daily_path), sep = '\n')
```
---

The interaction input file:
```{r, echo=FALSE, }
cat(readLines(interaction_path), sep = '\n')
```
---

The fish population file:
```{r, echo=FALSE, }
cat(readLines(fish_population_path), sep = '\n')
```
---

The fish parameter file:

---
```{r, echo=FALSE, }
cat(readLines(fish_parameters_path), sep = '\n')
```
---

The habitat parameter file:
```{r, echo=FALSE, }
cat(readLines(hab_path), sep = '\n')
```
---

The predator input file:
```{r, echo=FALSE, }
cat(readLines(predator_path), sep = '\n')
```
---
</font>
