---
output:  html_document
number_sections: true
title: "FHAST Habitat Summary"
header-includes:
    - \usepackage{setspace}\singlespacing
    - \usepackage{float}
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=0.2in
fontsize: 16pt
fig_caption: yes
indent: true
---
 <font size="4">

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, knitr::opts_chunk$set(warning = FALSE, message = FALSE))
library(here)

# Load Libraries
source(here("scripts","main","load_libraries.R"))

# Load some common functions used in running FHAST
# Load some file handling functions
source(here("scripts", "fhast_functions", "fhast_file_functions.R"))
# Load some file basic math functions
source(here("scripts", "fhast_functions", "fhast_math_functions.R"))
# Load some file basic biology functions
source(here("scripts", "fhast_functions", "fhast_biology_functions.R"))
# Load some plotting functions
source(here("scripts", "fhast_functions", "fhast_plot_functions.R"))

# Sets up the file structure for FHAST run
source(here("scripts", "main", "set_fhast_file_structure.R"))

# Run the initialization 
source(here("scripts","main","initialize_fhast.R"))

# Run again because of change in file path
input_path = read.table(file = here("temporary", "input_file_path.txt"),
                        col.names = "path")
initialize_fhast(input_path$path)

# load all the input files and make basic parameter files
# also do some basic checking of files
# need to load pathfinder finding first for adult parameters
source(here("scripts","migration", "pathfinding_functions.R"))

# make output locations 
source(here("scripts","main","make_output_folder.R"))

source(here("scripts","format_parameters","load_convert_parameters.R"))

```

```{r load_data, include=FALSE}

fish_migration_stats = readRDS(file = here("temporary",  "summary_migration_table.rds"))

fish_migration_map = here("temporary",  "migration_map.png")

fish_migration_hist = here("temporary",  "migration_energy_hist.png")

```

```{r pre_rrocess, include=FALSE}
predator_list =  unique(pred_model_params$species)
fish_list = unique(fish_parm$specie)
n = 0
```

### Simulation name: `r run_name`
***
## Tabular Outputs 
```{r print_fish_migration_stats, echo = FALSE}
fish_count <- length(unique(fish_migration_stats$species))

kable(fish_migration_stats,
      caption = paste0("The fish summary statistics for adult migration of the ", fish_count, " specie(s) of fish."),
      col.names = c("Species", "Energy Use (j)"))
```

\newpage
## Figures Outputs

```{r print_fish_migration_map, echo = FALSE, out.width = "100%", fig.align="center"}
knitr::include_graphics(fish_migration_map)
```
**Fig. `r (n = n + 1)`** A set of maps showing the most used migration paths for the adult migrants of the fish species (`r unique(fish_migration_stats$species)`). <br><br><br><br>

```{r print_fish_migration_hist, echo = FALSE, out.width = "100%", fig.align="center"}
knitr::include_graphics(fish_migration_hist)
```
**Fig. `r (n = n + 1)`** A set of histograms showing the energy expenditure for the adult migrants of the fish species (`r unique(fish_migration_stats$species)`). <br><br><br><br>

\newpage
## Appendix
### Run inputs
The main input file:
```{r, echo=FALSE}
cat(readLines(file.path(input_path$path)), sep = '\n')
```
---

The daily input file:
```{r, echo=FALSE, }
cat(readLines(daily_path), sep = '\n')
```
---

The interaction input file:
```{r, echo=FALSE, }
cat(readLines(interaction_path), sep = '\n')
```
---

The fish population file:
```{r, echo=FALSE, }
cat(readLines(fish_population_path), sep = '\n')
```
---

The fish parameter file:

---
```{r, echo=FALSE, }
cat(readLines(fish_parameters_path), sep = '\n')
```
---

The habitat parameter file:
```{r, echo=FALSE, }
cat(readLines(hab_path), sep = '\n')
```
---

The predator input file:
```{r, echo=FALSE, }
cat(readLines(predator_path), sep = '\n')
```
---
</font>
